\section{Question 10}
\horz

Let $H$ be a Hilbert space and $T\in \mathcal B(H).$ Suppose $X$ is a unitary operator in $\mathcal B(H).$ Then show that 
\begin{itemize}
\item[(i)] $\|X^{-1}TX\| = \|T\|.$
\item[(ii)] $T$ is normal if and only if $X^{-1}TX$ is normal.
\item[(iii)] $T$ is self adjoint if and only if $X^{-1}TX$ is self adjoint.
\item[(iv)] $T \geqslant 0$ if and only if $X^{-1}TX \geqslant 0.$
\item[(v)] $T$ is an orthogonal projection if and only if $X^{-1}TX$ is orthogonal projection. 
\end{itemize}
\horz

\begin{proof}
    Let $H$ be a Hilbert space and $T \in \calB \left( H \right)$. Let $X$ be a unitary operator in $\calB \left( H \right)$. 

    \begin{enumerate}[label=(\roman*)]
	\item We intend to show that $\norm{X^{-1}TX}=\norm{T}$. Since $X$ is a unitary operator, we have that $X$ is an isometric isomorphism.
	    To this end, let $f\in H$ and consider the following:
	    \begin{align*}
		\norm{X^{-1}TXf}^{2} &= \norm{X^{*}TXf}^{2} \\
		&= \ip{X^{*}TXf, X^{*}TXf} \\
		&= \ip{TXf, XX^{*}TXf} \\
		&= \ip{TXf, TXf} \\
		&= \norm{TXf}^{2}.
	    \end{align*}
	    Thus, we have that
	    \begin{equation}
		\norm{X^{-1}TXf} = \norm{TXf}
		\label{eqn:10.1}
	    \end{equation}
	    for each $f\in H$.
	    Now, we claim that
	    \begin{equation}
		\left\{ \norm{TXf} : \norm{f}=1 \right\} = \left\{ \norm{Tf} : \norm{f}=1 \right\}.
		\label{eqn:10.2}
	    \end{equation}
	    To prove this:
	    \begin{description}
		\item[$\left( \subset \right):$]  Let $y=\norm{TXf}$ for some $f \in H$ with $\norm{f}=1$. Since $X$ is a unitary operator, we have that $\norm{Xf}=\norm{f}=1$, hence, $y$ is in the set of the right side of the equality of the aforementioned claim.
		\item[$\left( \supset \right):$] Let $y=\norm{Tg}$ for some $g\in H$ with $\norm{g}=1$. Since $X$ is unitary, it is invertible and hence $Xf=g$ for some $f\in H$. Since $X$ is unitary, we have that $\norm{f}=\norm{Xf}=\norm{g}=1$. Thus, $y$ is in the left side of the set in the aforementioned equality.
	    \end{description}
	    Thus, we have 
	    \begin{align*}
		\norm{X^{*}TX} &= \sup_{\norm{f}=1} \norm{X^{*}TXf} & \text{(by definition)}\\
		&= \sup_{\norm{f}=1} \norm{TXf} & \text{(see \ref{eqn:10.1})}\\
		&= \sup_{\norm{f}=1} \norm{Tf} & \text{(see \ref{eqn:10.2})} \\
		&= \norm{T}. & \text{(by definition)}
	    \end{align*}
	    This completes the proof.
	\item 
	    \begin{description}
		\item[$\left( \Longrightarrow \right)$] Assume that $T$ is normal. Consider the following:
		    \begin{align*}
			\left( X^{*}TX \right)\left( X^{*}TX \right)^{*} &=  X^{*}TXX^{*}T^{*}X \\
			&= X^{*}TT^{*}X
		    \end{align*}

		    and on the other hand, we have
		    \begin{align*}
			\left( X^{*}TX \right)^{*} \left( X^{*}TX \right) &=  X^{*}TXX^{*}TX \\
			&= X^{*}TT^{*}X \\
		    \end{align*}
		    Note that the two computations above show that $X^{*}TX$ is normal by assuming $T$ is normal.
		\item[$\left( \Longleftarrow \right)$] The computation in the other direction, normality of $X^{*}TX$ and the invertibility of $X$ imply that $T$ is normal.
	    \end{description}
	    This completes the proof.
	\item 
	    \begin{description}
		\item[$\left( \Longrightarrow \right)$:] Suppose that $T$ is adjoint. To show that $X^{*}TX$ is self-adjoint, consider the following:
		    \begin{align*}
			\left( X^{*}TX \right)^{*} &= X^{*}T^{*}X \\
		&= X^{*}T X & (\text{using the fact that } T \text{is self-adjoint})
		    \end{align*}
		\item[$\left( \Longrightarrow \right)$] Suppose that $X^{*}TX$ is self-adjoint. To show $T$ is adjoint, consider the following:
		    \begin{align*}
			T^{*} &= XX^{*}T^{*}XX^{*} \\
			&= X\left( X^{*}TX \right)^{*} X^{*} \\
			&= XX^{*}TXX^{*} & (T\text{ is self-adjoint}) \\
			&= T.
		    \end{align*}
	    \end{description}

	\item 
	    \begin{description}
		\item[$\left( \Longrightarrow \right)$] Suppose that $T\ge 0$. The fact that $X^{*}TX$ is self-adjoint follows from item $\left( \text{iii} \right)$. Now, let $x\in H$. Consider the following:
		    \begin{align*}
			\ip{X^{*}TXx,x} &= \ip{TXx, Xx} \\
		    &\ge 0 & (\text{since } T \text{ is positive})
		    \end{align*}
		\item[$\left( \Longleftarrow \right)$] Suppose that $X^{*}TX\ge0$. The fact that $T$ is selfadjoint follows from item (iii). To complete the rest, let $f\in H$ and consider the following:
		    \begin{align*}
			\ip{Tx,x} &= \ip{XX^{*}TXX^{*}x,x} \\
			&= \ip{X^{*}TX(X^{*}x), X^{*}x} \\
		    & \ge 0 & (\text{since } X^{*}TX \ge 0)
		    \end{align*}
	    \end{description}

	\item First of all, note that item (iii) does half of the job. 
	    \begin{description}
		\item[$\left( \Longrightarrow \right)$] Suppose that $T$ is idempotent. Then we have that 
		    \begin{align*}
			\left( X^{*}TX \right)^{2} &=  X^{*}TXX^{*}TX \\
			&= X^{*}T^{2}X \\
			&= X^{*} TX & (T \text{ is idempotent})
		    \end{align*}
		\item[$\left( \Longleftarrow \right)$] Suppose that $X^{*}TX$ is idempotent. We wish to show that $T$ is idempotent. Observe that 
		    \begin{align*}
			T^{2} &=  TT \\
			&= XX^{*}TXX^{*}XX^{*} \\
			&= X\left( X^{*}TX \right)^{2}X^{*} \\
			&= X X^{*}TXX^{*} & (X^{*}TX \text{ is idempootent}) \\
			&= T.
		    \end{align*}
	    \end{description}
    \end{enumerate}

    This completes the entire proof.
\end{proof}
